My title

### 2022-03-21 outputs/paper/paper.Rmd

```{r crime-count-plot-by-education, fig.cap="Crime By Education Level", echo=FALSE, warning=FALSE, message = FALSE, fig.height=6, fig.width=8}
grid.arrange(university_crime_count,
            college_crime_count,
            elementary_crime_count,
            nrow=1)
```

>>>>

```{r crime-count-plot-by-education, fig.cap="Crime By Education Level", echo=FALSE, warning=FALSE, message = FALSE, fig.height=6, fig.width=8}
grid.arrange(university_crime_count,
            college_crime_count,
            elementary_crime_count,
            nrow=1)

# sex_crime_plot
```
